MP MetaAnalysis

### 2018-11-13 Paper_Analyses.Rmd
Comments on confirmatory results

CI_p <- function(x) paste0("(95% CI[", r2(x$ci.lb), ", ", r2(x$ci.ub), "], *p* ", psig(x$pval), ")")

@@

We should also point out that funnel plot asymmetry can be caused by multiple factors beside publication bias. The funnel plot asymmetry may also reflect heterogeneity in the data, perhaps due to some studies investigating more subtle effects than other studies.  [CHRISTINA: I have to add some bits here.]

@@

#Now we can actually make the funnel plot.
#Using your original data-frame, map standard error to your x-axis (for now) and Zr to your y-axis
fp_co = ggplot(aes(x = se, y = yi), data = dat_co) +
  #Regression line for the FP asymmetry
  geom_smooth(aes(x = se, y = yi), method = "lm", colour = "darkgrey", alpha = .5, se = FALSE, data = dat_co) +
  #Add your data-points to the scatterplot
  geom_point(size = 2.5, colour="black") +
  #
  #Give the x- and y- axes informative labels
  xlab('Standard Error') + ylab('Hedge\'s g')+
  # give it a title
    ggtitle("Correct") +
    # make sure both plots have same scale
    # still ylim because we haven't flipped yet
    #coord_cartesian(ylim = c(0.5, 0))+
  #Now using the 'dfCI' data-frame we created, plot dotted lines corresponding
  #to the lower and upper limits of your 95% CI region
  #And dashed lines corresponding to your 99% CI region
  #Add lines corresponding to 0 and estimate
  geom_line(aes(x = se.seq_co, y = 0), linetype = 'solid', data = dfCI_co) +
  geom_line(aes(x = se.seq_co, y = estimate_co), linetype = 'dashed', data = dfCI_co) +
  geom_line(aes(x = se.seq_co, y = ll95_co), linetype = 'dotted', data = dfCI_co) +
  geom_line(aes(x = se.seq_co, y = ul95_co), linetype = 'dotted', data = dfCI_co) +
  #  geom_line(aes(x = se.seq, y = ll99), linetype = 'dashed', data = dfCI) +
  #  geom_line(aes(x = se.seq, y = ul99), linetype = 'dashed', data = dfCI) +
  #Now plot dotted lines corresponding to the 95% CI of your meta-analytic estimate
  #geom_segment(aes(x = min(se.seq), y = meanll95, xend = max(se.seq), yend = meanll95), linetype='dotted', data=dfCI) +
  #geom_segment(aes(x = min(se.seq), y = meanul95, xend = max(se.seq), yend = meanul95), linetype='dotted', data=dfCI) +
  #Reverse the x-axis ordering (se) so that the tip of the funnel will appear
  #at the top of the figure once we swap the x- and y-axes...
  scale_x_reverse()+
  #Specify the range and interval for the tick-marks of the y-axis (Zr);
  #Choose values that work for you based on your data
  #scale_y_continuous(breaks=seq(-.45,0.8,0.25))+
  #And now we flip the axes so that SE is on y- and Zr is on x-
  coord_flip()+
  #Finally, apply my APA-format theme (see code at end of post).
  #You could, alternatively, specify theme_bw() instead.
  funnel_theme

@@

  #Now we can actually make the funnel plot.
  #Using your original data-frame, map standard error to your x-axis (for now) and Zr to your y-axis
  fp_mp = ggplot(aes(x = se, y = yi), data = dat_mp) +
    #Regression line for the FP asymmetry
    geom_smooth(aes(x = se, y = yi), method = "lm", colour = "darkgrey", alpha = .5, se = FALSE, data = dat_mp) +
    #Add your data-points to the scatterplot
    geom_point(size = 2.5, colour="black") +
    #
  #Give the x- and y- axes informative labels
  xlab('Standard Error') + 
    # remove y label because it will be combined with the other funnel plot
    ylab('Hedge\'s g')+
    # give it a title
    ggtitle("Mispronunciation") +
    # make sure both plots have same scale
    # still xlim because we haven't flipped yet
    #coord_cartesian(xlim = c(0.5, 1))+
    #Now using the 'dfCI' data-frame we created, plot dotted lines corresponding
    #to the lower and upper limits of your 95% CI region
    #And dashed lines corresponding to your 99% CI region
    #Add lines corresponding to 0 and estimate
    geom_line(aes(x = se.seq_mp, y = 0), linetype = 'solid', data = dfCI_mp) +
    geom_line(aes(x = se.seq_mp, y = estimate_mp), linetype = 'dashed', data = dfCI_mp) +
    geom_line(aes(x = se.seq_mp, y = ll95_mp), linetype = 'dotted', data = dfCI_mp) +
    geom_line(aes(x = se.seq_mp, y = ul95_mp), linetype = 'dotted', data = dfCI_mp) +
    #  geom_line(aes(x = se.seq, y = ll99), linetype = 'dashed', data = dfCI) +
    #  geom_line(aes(x = se.seq, y = ul99), linetype = 'dashed', data = dfCI) +
    #Now plot dotted lines corresponding to the 95% CI of your meta-analytic estimate
    #geom_segment(aes(x = min(se.seq), y = meanll95, xend = max(se.seq), yend = meanll95), linetype='dotted', data=dfCI) +
    #geom_segment(aes(x = min(se.seq), y = meanul95, xend = max(se.seq), yend = meanul95), linetype='dotted', data=dfCI) +
    #Reverse the x-axis ordering (se) so that the tip of the funnel will appear
    #at the top of the figure once we swap the x- and y-axes...
    scale_x_reverse()+
    #Specify the range and interval for the tick-marks of the y-axis (Zr);
    #Choose values that work for you based on your data
    #scale_y_mpntinuous(breaks=seq(-.45,0.8,0.25))+
    #And now we flip the axes so that SE is on y- and Zr is on x-
    coord_flip()+
    #Finally, apply my APA-format theme (see previous).
    #You could, alternatively, specify theme_bw() instead.
    funnel_theme +
    theme(axis.title.y = element_blank())

@@

We next examined the p-curves for significant values from the correctly pronounced and mispronounced conditions. The p-curve based on `r pcd_correct$ksig` statistically significant values for correct pronunciations indicates that the data contain evidential value (Z = `r r2(pcd_correct$Zppr)`, *p* `r psig(pcd_correct$p.Zppr)`) and there is no evidence of a large proportion of p-values just below the typical alpha threshold of .05. The p-curve based on `r pcd_misp$ksig` statistically significant values for mispronunciations indicates that the data contain evidential value (Z = `r r2(pcd_misp$Zppr)`, *p* `r psig(pcd_misp$p.Zppr)`) and there is no evidence of a large proportion of p-values just below the typical alpha threshold of .05.

Taken together, the results suggest a tendency in the literature towards publication bias. As a result, our meta-analysis may systematically overestimate effect sizes and we therefore interpret all estimates with caution. Yet, the p-curve analysis suggests that overall, the literature contains evidential value, reflecting a "real" effect. We therefore continue our meta-analysis.

@@

We first calculated the meta-analytic effect for object identification, i.e. looks to the target image in response to correctly pronounced words. The variance-weighted meta-analytic effect size Hedges' *g* was `r g_SE(sum_eff)` which was significantly different from zero `r CI_p(sum_eff)`. This is a rather large effect size (according to the criteria set by Cohen, 1988; see also Bergmann, et al., 2018; for comparative meta-analytic effect sizes in language acquisition research). That the effect size is significantly above zero suggests that when presented with the correctly pronounced label, infants fixated the corresponding object. Our analysis of funnel plot asymmetry, however, found evidence for publication bias, which might lead to an overestimated effect sizes as smaller, non-significant results might not be published. Although the effect size Hedges' *g* may be overestimated for object identification in response to correctly pronounced words, the p-curve results and a CI lower bound of `r r2(sum_eff$ci.lb)` suggests that this result is robust even when correcting for publication bias. In other words, we are confident that the true population mean lies above zero for object recognition of correctly pronounced words.

[CHRISTINA: Can you explain what the CI lower bound means here? I don't follow.]
[KATIE: What do you think about this (last sentence)? The CI lower bound stuff here actually comes from something you wrote, so tell me whether its correct.]

@@

Heterogeneity was significant for both correctly pronounced (Q(103) = `r r2(rma_correct$QE)`, *p* `r psig(rma_correct$QEp)`) and mispronounced words, (Q(146) = `r r2(rma_MP$QE)`, *p* `r psig(rma_MP$QEp)`). This indicated that the sample contains unexplained variance leading to significant difference across our studies beyond what is to be expected based on random sampling error. We therefore continue with our moderator analysis.

@@

The above two analyses considered the data from mispronounced and correctly pronounced words separately. To evaluate mispronunciation sensitivity, we  compared the effect size Hedges' *g* for correct pronunciations with mispronunciations directly, merging the two datasets. The moderator test was significant, `r mod_test(rma_MPeffect)`.  Hedges' *g* for mispronunciation sensitivity was `r g_SE(sum_eff)`, which indicated that the responses across conditions were significantly different `r CI_p(sum_eff)`. This confirms that although infants fixate the correct object for both correct pronunciations and mispronunciations, the observed fixations to target (as measured by the effect sizes) were significantly greater for correct pronunciations. In other words, we observe a significant difference between the two conditions and can now quantify the modulation of fixation behavior in terms of standardized effect sizes.

@@

To evaluate the different predictions we laid out in the introduction for how mispronunciation sensitivity will change as infants develop, we next added the moderator age (centered, in days). In the first analyses, we investigate the impact of age separately on conditions where words were either pronounced correctly or not. Age did not significantly modulate object identification in response to correctly pronounced `r mod_test(rma_correct_age)` or mispronounce words `r mod_test(rma_MP_age)`. The lack of a significant modulation together with the small estimates indicates that there was no relationship between age and target looks in response to a correctly pronounced or mispronounced label. This relationship is plotted in Figure 2.

@@

We then examined the interaction between age and mispronunciation sensitivity (correct vs. mispronounced words) in our whole dataset. The moderator test was significant `r mod_test(rma_MPeffect_age)`. This result is in line with the general observation that as infants mature they become better at language processing. The interaction between age and mispronunciation sensitivity, however, was not significant $\beta$`r full_estimate(sum_eff)`. The small estimate size, as well as inspection of Figure 2 suggests that as infants age, their mispronunciation sensitivity remains the same.

@@

p.diff <- ggplot(dat.cm, aes(mean_age_1/30.44, Misp_sensitivity)) + 
  ggtitle("b. Mispronunciation Sensitivity")+
  geom_point(aes(size = n_1),show.legend=FALSE, alpha = .5) + 
  geom_line(y= 0, linetype="dotted") + 
  geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=n_1)) +
  scale_colour_manual(values=cbPalette)+
  apatheme +
  theme(legend.title = element_blank(),
        legend.position = "bottom") + 
  xlab("Age in months") + 
  ylab("Mispronunciation Sensitivity")

@@

Of the `r n_distinct(dat$short_cite)` papers included in the meta-analysis, `r with(vi2, papers[has_vocab == "vocab"])` (comprehension = `r with(vi1, papers[has_vocab == "comprehension"])` papers; production = `r with(vi1, papers[has_vocab == "production"])`) analyzed the relationship between vocabulary scores and mispronunciation sensitivity, specifically object recognition for correct pronunciations and mispronunciations. There is reason to believe that production data are different from comprehension data (the former being easier to estimate for parents in the typical questionnaire-based assessment), so we analyze this data separately.

[CHRISTINA] SO WE DON'T WANT TO INTERPRET THE FIXED EFFECTS MODEL AT ALL, IT IS NOT SUITABLE BECAUSE THERE IS VARIANCE BETWEEN EVERY RECORD (LANGUAGE ETC).
I WOULD INTERPRET THE OVERALL CORRELATION AND THE CI, NOT THE P-VALUE (IN GENERAL). I ALSO WONDER WHETHER WE SHOULD MOVE THE SUBSET ANALYSES TO THE SUPPLEMENTARY MATERIALS AND JUST SAY OVERALL WE SEE NO RELATIONSHIPS AND CORRELATION COEFFICIENTS CONSISTENYL BELOW .1
WE THEREFORE MUST CONCLUDE THAT WITHIN NARROW AGE GROUPS VOCABULARY DOES NOT INFLUENCE ANYTHING WE LOOK AT. WE CANNOT DO THIS ANALYSIS FPOR MP SENSITIVITY BECAUSE WE DON'T HAVE THE NECESSARY RAW DATA.
[KATIE: Ah, so because for each paper the correlation and CI values straddle 0, this indicates that there really isn't much evidence for a relationship? I've tried to write this out below, let me know what you think. Over the summer, I had also played around with looking at how collection of vocabulary data has dropped off over the years, even though more mispronunciation studies have been published. That might be something interesting to add. If we truly think that this is what is driving the development of mispronunciation sensitivity, then why are people not collecting this data?]
(BUT I WONDER WHETHER WECOULD ENCODE THE REPORTED INTERACTION TERMS AND THE CORRELATION AND THEN DO SOMETHING WITH THAT?)
[KATIE: I'm not really sure what you mean by this :(]

@@

[Katie: below, I'm using coweeta.uga.edu/publications/10436.pdf, page 80 as a model for writing up these results. I haven't the funniest clue what I'm doing! :p]

We first considered the relationship between vocabulary and object recognition for correct pronunciations. Higher comprehension scores were associated with greater object recognition in response to correct pronunciations for 9 of 12 experimental conditions, with correlation values ranging from -0.17 to 0.48. The mean effect size XXX was 0.0897, but did not differ significantly from zero (95% CI[-0.0105; 0.1900] *p* = .0795). Higher production scores were also associated with greater object recognition in response to correct pronunciations for 9 of 16 experimental conditions, with correlation values ranging from -0.23 to 0.44. The mean effect size XXX was 0.0601, but did not differ significantly from zero (95% CI[-0.0331; 0.1533] *p* = .2061). For both comprehension and production scores, the small correlation effect sizes and large variances suggest a lack of relationship between vocabulary and object recognition for correct pronunciations.

@@

We next considered the relationship between vocabulary and object recognition for mispronunciations. Higher comprehension scores were associated with greater object recognition in response to correct pronunciations for 17 of 31 experimental conditions, with correlation values ranging from -0.35 to 0.57. The mean effect size XXX was 0.0377, but did not differ significantly from zero (95% CI[-0.0260; 0.1014] *p* = .2465). For production, however, lower production scores were associated with greater object recognition in response to mispronunciations for 16 of 31 experimental conditions, with correlation values ranging from -0.28 to 0.44. The mean effect size XXX was -0.0402, but did not differ significantly from zero (95% CI[-0.1043; 0.0238] *p* = .2181). For both comprehension and production scores, the small correlation effect sizes and large variances suggest a lack of relationship between vocabulary and object recognition for mispronunciations.

@@

The main goal of this paper was to assess mispronunciation sensitivity and its maturation with age. The results are clear: Although infants consider a mispronunciation as a better match with the target image than a distractor image, there was a consistent effect of mispronunciation sensitivity. This did not change with development. Of the 3 predictions and assumptions about the development of infants' sensitivity to mispronunciations discussed in the Introduction, the present results lend some support for the argument that mispronunciation sensitivity stays consistent as infants develop. This runs counter to existing theories of phono-lexical development, which predict either an increase (PRIMR ref) or decrease (Assim Model ref) in mispronunciation sensitivity. Furthermore, counter to the predictions for the PRIMR (PRIMR ref) and Assimilation(Assim ref) models, we found no relationship between vocabulary and target looking for correct pronunciations or mispronunciations. In sum, it seems that current theories of infants' phono-lexical development cannot fully capture our results and should be reconsidered with all the evidence in mind.

Alternatively, it is possible that variation in the analysis approach lead to systematic differences in the size of mispronunciation sensitivity. Choices about the approach to data analysis have a higher possibility to be influenced by the shape of the data itself after collection, and are therefore susceptible to a higher rate of false-positives (Simmons, Nelson, & Simonsohn, 2011). Although we did not have specific predictions about these variables, such as size of time window analyzed or dependent variable calculated, we included these variables in our coding scheme for the meta-analysis dataset. As reported in the Methods section (and discussed in detail below), some of these variables varied widely across studies. In the following section, we include an exploratory analysis to investigate the possibility of systematic differences in the approach to analysis in general and across infant age.

[KATIE] I've changed the above paragraph to lead to exploratory analyses, not moderators. Since the fmailiar/unfamiliar analysis doesn't really work out except for if we kind of subset and torture the data, I think its more interesting to talk about how choices of analysis / researcher degrees of freedom may influence the data

>>>>

CI_p <- function(x) paste0("(CI [", r2(x$ci.lb), ", ", r2(x$ci.ub), "], *p* ", psig(x$pval), ")")

@@

We should also point out that funnel plot asymmetry can be caused by multiple factors beside publication bias. The funnel plot asymmetry may also reflect heterogeneity in the data. There are various possible sources of heterogeneity, which our subsequent moderator analyses will begin to address. Nonetheless, we will remain cautious in our interpretation of our findings and hope that an open dataset that can be expanded by the community will attract previously unpublished null results so we can better understand infants' developing mispronunciation sensitivity.

@@

#Now we can actually make the funnel plot.
#Using your original data-frame, map standard error to your x-axis (for now) and Zr to your y-axis
fp_co = ggplot(aes(x = se, y = yi), data = dat_co) +
  #Regression line for the FP asymmetry
  geom_smooth(aes(x = se, y = yi), method = "lm", colour = "darkgrey", alpha = .5, se = FALSE, data = dat_co) +
  #Add your data-points to the scatterplot
  geom_point(size = 2.5, colour="black") +
  #
  #Give the x- and y- axes informative labels
  xlab('Standard Error') + ylab('Hedges\' g')+
  # give it a title
    ggtitle("Correct") +
    # make sure both plots have same scale
    # still ylim because we haven't flipped yet
    #coord_cartesian(ylim = c(0.5, 0))+
  #Now using the 'dfCI' data-frame we created, plot dotted lines corresponding
  #to the lower and upper limits of your 95% CI region
  #And dashed lines corresponding to your 99% CI region
  #Add lines corresponding to 0 and estimate
  geom_line(aes(x = se.seq_co, y = 0), linetype = 'solid', data = dfCI_co) +
  geom_line(aes(x = se.seq_co, y = estimate_co), linetype = 'dashed', data = dfCI_co) +
  geom_line(aes(x = se.seq_co, y = ll95_co), linetype = 'dotted', data = dfCI_co) +
  geom_line(aes(x = se.seq_co, y = ul95_co), linetype = 'dotted', data = dfCI_co) +
  #  geom_line(aes(x = se.seq, y = ll99), linetype = 'dashed', data = dfCI) +
  #  geom_line(aes(x = se.seq, y = ul99), linetype = 'dashed', data = dfCI) +
  #Now plot dotted lines corresponding to the 95% CI of your meta-analytic estimate
  #geom_segment(aes(x = min(se.seq), y = meanll95, xend = max(se.seq), yend = meanll95), linetype='dotted', data=dfCI) +
  #geom_segment(aes(x = min(se.seq), y = meanul95, xend = max(se.seq), yend = meanul95), linetype='dotted', data=dfCI) +
  #Reverse the x-axis ordering (se) so that the tip of the funnel will appear
  #at the top of the figure once we swap the x- and y-axes...
  scale_x_reverse()+
  #Specify the range and interval for the tick-marks of the y-axis (Zr);
  #Choose values that work for you based on your data
  #scale_y_continuous(breaks=seq(-.45,0.8,0.25))+
  #And now we flip the axes so that SE is on y- and Zr is on x-
  coord_flip()+
  #Finally, apply my APA-format theme (see code at end of post).
  #You could, alternatively, specify theme_bw() instead.
  funnel_theme

@@

  #Now we can actually make the funnel plot.
  #Using your original data-frame, map standard error to your x-axis (for now) and Zr to your y-axis
  fp_mp = ggplot(aes(x = se, y = yi), data = dat_mp) +
    #Regression line for the FP asymmetry
    geom_smooth(aes(x = se, y = yi), method = "lm", colour = "darkgrey", alpha = .5, se = FALSE, data = dat_mp) +
    #Add your data-points to the scatterplot
    geom_point(size = 2.5, colour="black") +
    #
  #Give the x- and y- axes informative labels
  xlab('Standard Error') + 
    # remove y label because it will be combined with the other funnel plot
    ylab('Hedges\' g')+
    # give it a title
    ggtitle("Mispronunciation") +
    # make sure both plots have same scale
    # still xlim because we haven't flipped yet
    #coord_cartesian(xlim = c(0.5, 1))+
    #Now using the 'dfCI' data-frame we created, plot dotted lines corresponding
    #to the lower and upper limits of your 95% CI region
    #And dashed lines corresponding to your 99% CI region
    #Add lines corresponding to 0 and estimate
    geom_line(aes(x = se.seq_mp, y = 0), linetype = 'solid', data = dfCI_mp) +
    geom_line(aes(x = se.seq_mp, y = estimate_mp), linetype = 'dashed', data = dfCI_mp) +
    geom_line(aes(x = se.seq_mp, y = ll95_mp), linetype = 'dotted', data = dfCI_mp) +
    geom_line(aes(x = se.seq_mp, y = ul95_mp), linetype = 'dotted', data = dfCI_mp) +
    #  geom_line(aes(x = se.seq, y = ll99), linetype = 'dashed', data = dfCI) +
    #  geom_line(aes(x = se.seq, y = ul99), linetype = 'dashed', data = dfCI) +
    #Now plot dotted lines corresponding to the 95% CI of your meta-analytic estimate
    #geom_segment(aes(x = min(se.seq), y = meanll95, xend = max(se.seq), yend = meanll95), linetype='dotted', data=dfCI) +
    #geom_segment(aes(x = min(se.seq), y = meanul95, xend = max(se.seq), yend = meanul95), linetype='dotted', data=dfCI) +
    #Reverse the x-axis ordering (se) so that the tip of the funnel will appear
    #at the top of the figure once we swap the x- and y-axes...
    scale_x_reverse()+
    #Specify the range and interval for the tick-marks of the y-axis (Zr);
    #Choose values that work for you based on your data
    #scale_y_mpntinuous(breaks=seq(-.45,0.8,0.25))+
    #And now we flip the axes so that SE is on y- and Zr is on x-
    coord_flip()+
    #Finally, apply my APA-format theme (see previous).
    #You could, alternatively, specify theme_bw() instead.
    funnel_theme +
    theme(axis.title.y = element_blank())

@@

We next examined the p-curves for significant values from the correctly pronounced and mispronounced conditions. The p-curve based on `r pcd_correct$ksig` statistically significant values for correct pronunciations indicates that the data contain evidential value (Z = `r r2(pcd_correct$Zppr)`, *p* `r psig(pcd_correct$p.Zppr)`) and we find no evidence of a large proportion of p-values just below the typical alpha threshold of .05 that researchers consistently apply in this line of research. The p-curve based on `r pcd_misp$ksig` statistically significant values for mispronunciations indicates that the data contain evidential value (Z = `r r2(pcd_misp$Zppr)`, *p* `r psig(pcd_misp$p.Zppr)`) and there is again no evidence of a large proportion of p-values just below the typical alpha threshold of .05.

Taken together, the results suggest a tendency in the literature towards publication bias. As a result, our meta-analysis may systematically overestimate effect sizes and we therefore interpret all estimates with caution. Yet, the p-curve analysis suggests that the literature contains evidential value, reflecting a "real" effect. We therefore continue our meta-analysis.

@@

We first calculated the meta-analytic effect for infants' ability to identify objects when hearing correctly pronounced labels. The variance-weighted meta-analytic effect size Hedges' *g* was `r g_SE(sum_eff)` which was significantly different from zero `r CI_p(sum_eff)`. This is a rather large effect size (according to the criteria set by Cohen, 1988; see also Bergmann, et al., 2018; for comparative meta-analytic effect sizes in language acquisition research). That the effect size is significantly above zero suggests that when presented with the correctly pronounced label, infants fixated the corresponding object. Our analysis of funnel plot asymmetry, however, found evidence for publication bias, which might lead to an overestimated effect sizes as smaller, non-significant results might not be published despite the fact that they should occur regularly even in well-powered studies. Although the effect size Hedges' *g* may be overestimated for object identification in response to correctly pronounced words, the p-curve results and a CI lower bound of `r r2(sum_eff$ci.lb)` which is substantially above zero suggests that this result should be robust even when correcting for publication bias. In other words, we are confident that the true population mean lies above zero for object recognition of correctly pronounced words.

@@

Heterogeneity was significant for both correctly pronounced (Q(103) = `r r2(rma_correct$QE)`, *p* `r psig(rma_correct$QEp)`) and mispronounced words, (Q(146) = `r r2(rma_MP$QE)`, *p* `r psig(rma_MP$QEp)`). This indicated that the sample contains unexplained variance leading to significant difference across our studies beyond what is to be expected based on random sampling error. We therefore continue with our moderator analysis to investigate possible sources of this variance.

[Christina] I am not sure about the placement of this paragraph because the next section cannot explain this heterogeneity, so maybe we should move it down to the beginning of the age part?

@@

The above two analyses considered the data from mispronounced and correctly pronounced words separately. To evaluate mispronunciation sensitivity, we compared the effect size Hedges' *g* for correct pronunciations with mispronunciations directly. To this end, we combined the two datasets. The moderator test was significant, `r mod_test(rma_MPeffect)`. The estimate for mispronunciation sensitivity was `r g_SE(sum_eff)`, and infants' looking times across conditions were significantly different `r CI_p(sum_eff)`. This confirms that although infants fixate the correct object for both correct pronunciations and mispronunciations, the observed fixations to target (as measured by the effect sizes) were significantly greater for correct pronunciations. In other words, we observe a significant difference between the two conditions and can now quantify the modulation of fixation behavior in terms of standardized effect sizes and their variance. This first result has both theoretical and practical implications, as we can now reason about the amount of perturbance caused by mispronunciations and can plan future studies to further investigate this effect with suitable power.

@@

To evaluate the different predictions we laid out in the introduction for how mispronunciation sensitivity will change as infants develop, we next added the moderator age (centered, in days). 
[Christina] What about the whole months thing?

In the first analyses, we investigate the impact of age separately on conditions where words were either pronounced correctly or not. Age did not significantly modulate object identification in response to correctly pronounced (`r mod_test(rma_correct_age)`) or mispronounce words (`r mod_test(rma_MP_age)`). The lack of a significant modulation together with the small estimates indicates that there was no relationship between age and target looks in response to a correctly pronounced or mispronounced label. This relationship is plotted in Figure 2.

[Christina] OK there is a mismatch between what you write and the numbers, can you verify?

@@

We then examined the interaction between age and mispronunciation sensitivity (correct vs. mispronounced words) in our whole dataset. The moderator test was significant (`r mod_test(rma_MPeffect_age)`). The interaction between age and mispronunciation sensitivity, however, was not significant ($\beta$ `r full_estimate(sum_eff)`), pointing to the moderator test being driven by the difference between conditions. The small estimate, as well as inspection of Figure 2 suggests that as infants age, their mispronunciation sensitivity remains the same.

@@

p.diff <- ggplot(dat.cm, aes(mean_age_1/30.44, Misp_sensitivity)) + 
  ggtitle("b. Mispronunciation Sensitivity")+
  geom_point(aes(size = n_1/2),show.legend=FALSE, alpha = .3) + 
  geom_line(y= 0, linetype="dotted") + 
  geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=n_1), color = "black") +
  scale_colour_manual(values=cbPalette)+
  apatheme +
  theme(legend.title = element_blank(),
        legend.position = "bottom") + 
  xlab("Age in months") + 
  ylab("Mispronunciation Sensitivity")

@@

Of the `r n_distinct(dat$short_cite)` papers included in the meta-analysis, `r with(vi2, papers[has_vocab == "vocab"])` analyzed the relationship between vocabulary scores and object recognition for correct pronunciations and mispronunciations (comprehension = `r with(vi1, papers[has_vocab == "comprehension"])` papers; production = `r with(vi1, papers[has_vocab == "production"])`). There is reason to believe that production data are different from comprehension data (the former being easier to estimate for parents in the typical questionnaire-based assessment), so we analyze this data separately.

[Christina] Removed the previous comment chaos.
So can you not only list papers but also n conditions above? With just 1 paper for production, I wouldn't analyze it to be honest. it's just not enough data. 
I also liked your comments about the time line of this whole thing, can you extract the years of papers which report this? Might be extremely useful in the discussion and strengthens our case that there is no effect, bc people don't find the predicted relation with vocab. 
Also, cann you add a citation for comp vs prod? I think Evan Kidd had a paper on it, if you don't have one handy, I can look it up.

@@

[Katie: below, I'm using coweeta.uga.edu/publications/10436.pdf, page 80 as a model for writing up these results. I haven't the funniest clue what I'm doing! :p]
[Christina] looks good to me.

We first considered the relationship between vocabulary and object recognition for correct pronunciations. Higher comprehension scores were associated with greater object recognition in response to correct pronunciations for 9 of 12 experimental conditions, with correlation values ranging from -0.17 to 0.48. The mean effect size XXX was small with 0.0897, which did not differ significantly from zero (CI [-0.0105; 0.1900] *p* = .0795). However, the lower bound of the CI is close to zero, and one might hypothesize that with more power the small relationship might become significant. At the same time, a larger sample might confirm our conclusion that there is no relationship.

Higher production scores were also associated with greater object recognition in response to correct pronunciations for 9 of 16 experimental conditions, with correlation values ranging from -0.23 to 0.44. The mean effect size XXX was again small and not significantly different from zero with 0.0601 (CI [-0.0331; 0.1533] *p* = .2061). For both comprehension and production scores, the small correlation effect sizes and large variances suggest a lack of relationship between vocabulary and object recognition for correct pronunciations. However, we note again that comparatively few studies report the correlation between vocabulary and infants' responses to correct pronunciations to begin with and thus we cannot draw any firm conclusions based on this small sample of studies.

[Christina] I think bc the effect is small but apparently consistent, we can reason that we might have a power problem and thus cannot draw firm conclusions.

@@

We next considered the relationship between vocabulary and object recognition for mispronunciations. Higher comprehension scores were associated with greater object recognition in response to correct pronunciations for 17 of 31 experimental conditions, with correlation values ranging from -0.35 to 0.57. The mean effect size XXX was 0.0377, but did not differ significantly from zero (CI[-0.0260; 0.1014] *p* = .2465). For production, however, lower production scores were associated with greater object recognition in response to mispronunciations for 16 of 31 experimental conditions, with correlation values ranging from -0.28 to 0.44. The mean effect size XXX was -0.0402, (CI [-0.1043; 0.0238] *p* = .2181). For both comprehension and production scores, the small correlations and large variances suggest a lack of relationship between vocabulary and object recognition for mispronunciations. We again emphasize that we cannot draw firm conclusions due to the small number of studies we were able to include here.

[Christina] Is there a reason the above numbers aren't read out as before?
Also, I think the effect size is pearson's r, because that's what we put in, right?

@@

The main goal of this paper was to assess mispronunciation sensitivity and its maturation with age. The results seem clear: Although infants consider a mispronunciation as a better match with the target image than a distractor image, there was a consistent effect of mispronunciation sensitivity. This did not change with development. Of the 3 predictions and assumptions about the development of infants' sensitivity to mispronunciations discussed in the Introduction, the present results lend some support for the argument that mispronunciation sensitivity stays consistent as infants develop. This runs counter to existing theories of phono-lexical development, which predict either an increase (PRIMR ref) or decrease (Assim Model ref) in mispronunciation sensitivity. Furthermore, counter to the predictions for the PRIMR (PRIMR ref) and Assimilation(Assim ref) models, we found no relationship between vocabulary and target looking for correct pronunciations or mispronunciations. In sum, it seems that current theories of infants' phono-lexical development cannot fully capture our results and should be reconsidered with all the evidence in mind.

Alternatively, an effect of maturation might have been masked by other factors we have not yet captured in our analyses. A strong candidate that emerged during the construction of the present dataset and careful reading of the original papers is the analysis approach. We observed, as mentioned in the Methods section, large variance in the dependent variable reported, and additionally noted variance in the time window chosen for analyses. Researchers might adapt their analysis strategy to age or they might be influenced by having observed the data. In the latter case, we expect an increase in significant results, which at the same time can (partially) explain the publication bias we observe (Simmons, Nelson, & Simonsohn, 2011).

We included size of time window analyzed or dependent variable calculated in our coding of the dataset because they are consistently reported and might be useful for experiment design in the future by highlighting typical choices and helping establish field standards. In the following section, we include an exploratory analysis to investigate the possibility of systematic differences in the approach to analysis in general and across infant age. Our analyses will show that a standard, a priori registered analysis of looking while listening paradigms is needed and can improve the health of a currently biased literature.

[Christina] The last sentence is a bit clunky, please improve.
